\mytitle

### 2015-07-28 O3CycleScheme.tex
Minor changes

\documentclass[]{standalone}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{graphicx}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

% Figures
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}
%\usepackage{chemfig}

% Tikz styles
\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
\tikzstyle{emp} = [draw=none,fill=none]
\tikzstyle{ar} = [->,draw=black!70,line width=2]
\tikzstyle{ln} = [-,draw=black!70,line width=2]

\begin{document}
\begin{tikzpicture}[node distance = 4cm, auto]

@@

\end{document}

>>>>

%\documentclass[]{standalone}
%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%
%\usepackage{graphicx}
%%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%
%% Figures
%\usepackage{tikz}
%\usetikzlibrary{shapes,arrows}
%\usetikzlibrary{positioning}
%\usetikzlibrary{calc}
%%\usepackage{chemfig}
%
%% Tikz styles
%\tikzstyle{reg} = [rounded rectangle, text width=2cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
%\tikzstyle{rad} = [rounded rectangle, draw=none, text width=2cm, fill=red!10, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]
%\tikzstyle{long} = [rounded rectangle, draw=none, text width=3.5cm, fill=black!5, align=center, anchor=west,font=\sffamily\Large\bfseries, minimum height=1cm, inner sep=0]   
%\tikzstyle{add} = [scale=1.5, draw=none,fill=none,align=center]
%\tikzstyle{emp} = [draw=none,fill=none]
%\tikzstyle{ar} = [->,draw=black!70,line width=2]
%\tikzstyle{ln} = [-,draw=black!70,line width=2]

%\begin{document}
\begin{tikzpicture}[node distance = 4cm, auto]

@@

%\end{document}
